BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2017-04-07 Paper2/BOAST.tex
passe FD-BV

\paragraph{Vectorization} The first proposed optimization involves computing
five pixels instead of one using the vectors available on the Mali
architecture. This is done using the native OpenCL support for vectorization.
For instance \emph{vload16} load 16 consecutive elements from memory and stores
it a vector.  Here the loaded vector is of type \emph{uchar16} meaning that it
is a vector of 16 consecutive bytes. In order to do computations without
overflowing, those vectors have to be converted (using \emph{convert\_int16}) to
a signed and bigger integer type.  Here they are converted to signed 4 bytes
integers, leading to a vector size of 64 bytes.

@@

Once this optimization space is designed, the user selects an optimization
strategy, brute force and genetic algorithm are provided by BOAST, or can
design his own. BOAST will then evaluate the different candidates generated by
the optimization program. The candidate's parameters define the output source
code that will be generated by BOAST (Step 2). The resulting code source is
then built according to the specified compiler and options (Step 3). The kernel
can be benchmarked and tested for non regression. Based on the results, other
optimizations can be selected (Step 4).The process can be repeated until a good
candidate is found on the target platform. The resulting kernel is then added
to the program (Step 5).

@@

%%% Porting SPECFEM3D to OpenCL using BOAST %%%
\subsection{Porting Application Kernels: Porting SPECFEM3D from CUDA to
OpenCL using BOAST\label{subsec:specfem}}

>>>>

\paragraph{Vectorization} The first proposed optimization involves computing
five pixels instead of one using the vectors available on the Mali
architecture. This is done using the native OpenCL support for vectorization.
For instance \emph{vload16} loads 16 consecutive elements from memory and stores
it in a vector.  Here the loaded vector is of type \emph{uchar16} meaning that it
is a vector of 16 consecutive bytes. In order to do computations without
overflowing, those vectors have to be converted (using \emph{convert\_int16}) to
a signed and bigger integer type.  Here they are converted to signed 4 bytes
integers, leading to a vector size of 64 bytes.

@@

Once this optimization space is designed, the user selects an optimization
strategy, brute force and genetic algorithms are provided by BOAST, or can
design his own. BOAST will then evaluate the different candidates generated by
the optimization program. The candidate's parameters define the output source
code that will be generated by BOAST (Step 2). The resulting code source is
then built according to the specified compiler and options (Step 3). The kernel
can be benchmarked and tested for non regression. Based on the results, other
optimizations can be selected (Step 4).The process can be repeated until a good
candidate is found on the target platform. The resulting kernel is then added
to the program (Step 5).

@@

%%% Porting SPECFEM3D to OpenCL using BOAST %%%
\subsection{Porting SPECFEM3D Application Kernels: from CUDA to OpenCL
using BOAST\label{subsec:specfem}}
